Hydra Battles and Cie

### 2021-02-12 doc/hydras.tex
reorganization of the index (in progress)

%\SetWatermarkLightness{0.8}
% \definecolor{lightorange}{rgb}{1,0.7,0.5}
% \SetWatermarkScale{0.35}
% \SetWatermarkText{Work in Progress}
% \SetWatermarkColor{lightorange}

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury\\ \emph{The formalization of primitive recursive functions was originally authored by Russel O'Connor}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

\section{How to Install the Libraries}
\label{sec:orgheadline4}
\begin{itemize}
\item The present distribution has been checked with version 8.12.0 of the Coq proof assistant, with the plug-ins \texttt{coq-paramcoq}, \texttt{coq-equations}
and \texttt{coq-mathcomp-algebra}.

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean,  Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmerman for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team at laBRI for their helpful comments 
on  oral presentations of this work.

@@

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main types and type classes}
\begin{tabular}{|c|c|c|l|}
\hline
Name & Description& Page \\\hline
ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main functions and constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& Canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& Helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
H\_ & H\_ alpha n & $H_\alpha(n)$ & Hardy's \texttt{H} fast growing hierarchy & \pageref{Functions:H-alpha} \\
L\_ & L\_ alpha k & $L_\alpha(k)$ & final step of a standard path & \pageref{Functions:L-alpha} \\
succ & succ alpha & & Successor & \pageref{Functions:succ-T1}, \pageref{Functions:succ-sch} \dots \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

>>>>

\SetWatermarkLightness{0.8}
\definecolor{lightorange}{rgb}{1,0.7,0.5}
\SetWatermarkScale{0.35}
\SetWatermarkText{Work in Progress}
\SetWatermarkColor{lightorange}

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \\with contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury\\ \emph{The formalization of primitive recursive functions was originally authored by Russel O'Connor}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

\section{How to Install the Libraries}
\label{sec:orgheadline4}
\begin{itemize}
\item The present distribution has been checked with version 8.13.0 of the Coq proof assistant, with the plug-ins \texttt{coq-paramcoq}, \texttt{coq-equations}
and \texttt{coq-mathcomp-algebra}.

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean,  Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmerman for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

@@

### 2021-02-12 doc/part-hydras.tex
reorganization of the index (in progress)

Technically, a \emph{hydra} is just a finite ordered tree, each node of which 
has any number of sons. Note that, contrary to the computer science tradition, we will show the hydras 
with the heads up and the foot (i.e., the root of the tree) down.
Fig.~\ref{fig:Hy} represents such  a hydra, which will be referred to as \texttt{Hy} in our examples (please look at the 
module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html}{Hydra.Hydra\_Examples}).

@@

If \texttt{OB} is presumed to be correct, the we can consider that \texttt{OA} ``inherits'' its correctness from the bigger notation system \texttt{OB}.

\label{types:SubON}
\index{hydras}{Library OrdinalNotations!Type classes!SunON}

@@

\label{types:ON-for}
\index{hydras}{Library OrdinalNotations}{Type classes!ON\_correct}

@@

\label{types:T1}
%\index{Constants!zero:T1}

@@

\subsection{Pretty Printing Ordinals in Cantor Normal Form}
\label{sect:ppT1}

@@

@@

\subsubsection{Canonical Sequences in Coq}

@@

\label{Functions:L-alpha}

\begin{Coqsrc}
From Equations Require Import Equations.
Require Import ArithRing Lia.

@@

\index{coq}{Plug-ins!Equations}
\label{Functions:H-alpha}

@@

\index{coq}{Plug-ins!Equations}
\label{Functions:F-alpha}
\index{maths}{Rapidly growing functions}

@@

>>>>

Technically, a \emph{hydra} is just a finite ordered tree, each node of which 
has any number of sons. Note that, contrary to the computer science tradition, we will show the hydras 
with the heads up and the foot (i.e., the root of the tree) down.
Fig.~\ref{fig:Hy} represents such  a hydra, which will be referred to as \texttt{Hy} in our examples (please look at the 
module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html}{Hydra.Hydra\_Examples}). 
\emph{For a less technical description of hydras, please see 
\url{https://www.smbc-comics.com/comic/hydra}.}

@@

If \texttt{OB} is presumed to be correct, then we may consider that \texttt{OA} ``inherits'' its correctness from the bigger notation system \texttt{OB}.

\label{types:SubON}
\index{hydras}{Library OrdinalNotations!Type classes!SubON}

@@

\label{types:ON-for}
\index{hydras}{Library OrdinalNotations!Type classes!ON\_correct}

@@

\label{types:T1}
%\index{Constants!zero:T1}
\index{hydras}{Library Epsilon0!Types!T1}

@@

\subsection{Pretty Printing Ordinals in Cantor Normal Form}
\label{sect:ppT1}
\index{hydras}{Library Epsilon0!Types!ppT1}

@@

\index{hydras}{Library Epsilon0!Functions!succ}

@@

\subsubsection{Canonical Sequences in Coq}
\index{hydras}{Library Epsilon0!Functions!canon}
\index{hydras}{Library Epsilon0!Functions!canonS}

@@

\label{Functions:L-alpha}
 \index{hydras}{Library Epsilon0!Functions!L\_@L\_ (final step of a minimal path}
\begin{Coqsrc}
From Equations Require Import Equations.
Require Import ArithRing Lia.

@@

\index{hydras}{Library Epsilon0!Functions!H\_@H\_ (Hardy hierarchy)}
\index{coq}{Plug-ins!Equations}
\label{Functions:H-alpha}

@@

\index{coq}{Plug-ins!Equations}
\label{Functions:F-alpha}
\index{maths}{Rapidly growing functions}
\index{hydras}{Library Epsilon0!Functions!F\_@F\_ (Wainer hierarchy)}

@@

\index{hydras}{Library Gamma0!Types!T2}
